Which spherical CNN should you use?\\ DeepSphere V2

### 2019-07-22 main.tex
small updates (mdeff)

\begin{abstract}
story / main point:

@@

Present the different spherical CNNs with pro and cons => mostly scale vs generality\\
* 2D CNN => doesn't respect geometry and equivariance\\
* Cohen spherical CNN => most general, but doesn't scale\\
* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)\\
* Esteves => ?
* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)\\

@@

\subsection{Convergence theorem}

@@

* define a measure of equiv error\\
* show convergence empirically\\
* improved upon V1\\
* no difference in practice (see experiment xx) => NNs are resilient to equiv error\\

\section{Experiments [2 pages]}
Which experience show that DeepSphere V1 and V2 are equivalent in practice.

@@

* same perf as other spherical CNNs, but 40 times faster
* compare the two samplings => not much difference

@@

other sphercial CNNs cannot scale to 10M pixels (tested on 10k at most)

@@

\subsubsection*{Author Contributions}
If you'd like to, you may include  a section for author contributions as is done
in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Use unnumbered third level headings for the acknowledgments. All
acknowledgments, including those to funding agencies, go at the end of the paper.

@@

{\LARGE \sc {Title of the paper: Supplementary Material}}
\appendix
\section{Proof of theorem}

>>>>

\begin{abstract}

story: there are tradeoffs when designing a spherical CNN

@@

Present the different spherical CNNs with pro and cons => mostly scale vs generality\\
* 2D CNN => doesn't respect geometry and equivariance\\
* Cohen spherical CNN => most general, but doesn't scale\\
* Cohen gauge => fixes scale, at the price of deformation (sphere => icosahedron)\\
* Esteves => ? \\
* Jiang => need a global coordinate system (ok for planets, not projections like cosmo)\\

@@

\subsection{HEALPix: convergence theorem}

\subsection{Equiangular}

explain rapidly Renata \& Pascal

@@

* define a measure of equiv error\\
* show convergence empirically (for Nside up to 1024) \\
* improved upon V1\\
* no difference in practice (see experiment xx) => NNs are resilient to equiv error\\

\section{Experiments [2 pages]}

Show: \\
* meet the desiderata \\
* DeepSphere V1 and V2 are equivalent in practice \\
* anisotropy doesn't help \\

@@

* same perf as other spherical CNNs, but 40 times faster \\
* compare the two samplings => not much difference \\

@@

* other sphercial CNNs cannot scale to 10M pixels (tested on 10k at most) \\
* redo the experiment with the optimal graph (cannot just copy the old results) and compare \\

@@

\newpage
\subsubsection*{Author Contributions}
Left blank for anonymity reason
% If you'd like to, you may include  a section for author contributions as is done
% in many journals. This is optional and at the discretion of the authors.

\subsubsection*{Acknowledgments}
Left blank for anonymity reason
% Use unnumbered third level headings for the acknowledgments. All
% acknowledgments, including those to funding agencies, go at the end of the paper.

@@

{\LARGE \sc {Title of the paper: Supplementary Material}}
\appendix

\section{Proof of theorem}
